Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 nge.tex
Pass on NGE experiments and scattered space savings
minor fixes and response to comment in 5.0.

\subsection{Rationale} \aanote{I think that the names of the states should be
removed. They are meaningless without the figures. I left them just in case we
decide to reintroduce the figures.}\mtnote{Done.}

\jhanote{admittedly i haven't read earlier section in question  carefully, but
i'm a bit confused about the use of "wide area". wide area is typically used for
cross data center}\mtnote{Every PanDA Pilot has to communicate with PanDA
Server. PanDA Server runs on dedicated resources, outside OLCF. Titan's worker
nodes cannot communicate with PanDA Server because their connectivity is limited
to Titan's network. Do you have a suggestion for an alternative to ``wide
area''?}

As seen in \S\ref{sec:panda_deployment}, PanDA Broker was deployed on DTNs
because of the absence of wide area network connectivity on Titan's worker
nodes. The lack of pilot capabilities impacts both the efficiency and the
flexibility of PanDA's execution process. Pilots could help to improve
efficiency by increasing throughput and by enabling better use of backfill
utilization. Further, pilots makes easier to support heterogeneous workloads.

As discussed in \S\ref{sec:panda_titan}, the absence of pilots imposes the
static coupling between MPI scripts submitted to the PBS batch system and
detector simulations. This makes impossible to schedule multiple generations of
workload on the same PBS job: Once a number of detector simulations are packaged
into a PBS job and this job is queued on Titan, no further simulations can be
added to that job. New simulations have to be packaged into a new PBS job that
needs to be submitted to Titan on the base of the backfill availability of that
moment.

The support of  multiple workload generations would enable a more efficient
use of the backfill availability of walltime. Currently, when a set of
simulations ends, the PBS job also ends, independent of whether more wall-time
would still be available. With a pilot, more simulations could be executed so
to utilize all the available wall-time, while avoiding further job packaging
and submission overheads.

@@

Multiple generations would also help with relaxing two assumptions of the
current execution model: knowing the number of simulations before submitting the
MPI script, and having a fixed amount of events per simulation (100 at the
moment). Pilots would enable the scheduling of simulations independently from
whether they were available at the moment of submitting the pilot. Further,
simulations with a varying number of events could be scheduled on a pilot,
depending on the amount of remaining walltime and the distribution of execution
time per event, as shown in \S\ref{ssec:panda_titan},
Figure~\ref{fig:100event-distrib}. This capabilities would be particularly
useful to increase the PanDA Broker efficiency for availabilities with a wide
delta between the number of cores and walltime.

@@

% -----------------------------------------------------------------------------
\subsection{Architecture}
\label{sec:arch}

>>>>

% \subsection{Rationale}
\aanote{I think that the names of the states should be removed. They are
meaningless without the figures. I left them just in case we decide to
reintroduce the figures.}\mtnote{Done.}

\jhanote{admittedly i haven't read earlier section in question  carefully, but
i'm a bit confused about the use of "wide area". wide area is typically used for
cross data center}\mtnote{Every PanDA Pilot has to communicate with PanDA
Server. PanDA Server runs on dedicated resources, outside OLCF. Titan's worker
nodes cannot communicate with PanDA Server because their connectivity is limited
to Titan's network. Do you have a suggestion for an alternative to ``wide
area''?} \jhanote{how is the following: "... deployed on the DTNs as Titan's worker
nodes lack connectivity to the wide area network"}.

As seen in \S\ref{sec:panda_deployment}, PanDA Broker was deployed on DTNs
because of the absence of wide area network connectivity on Titan's worker
nodes. The lack of pilot capabilities impacts both the efficiency and the
flexibility of PanDA's execution process. Pilots could help to improve
efficiency by increasing throughput and by enabling better use of backfill
utilization. Further, pilots makes it easier to support heterogeneous
workloads.

As discussed in \S\ref{sec:panda_titan}, the absence of pilots imposes the
static coupling between MPI scripts submitted to the PBS batch system and
detector simulations. This makes the scheduling of multiple generations of
workload on the same PBS job impossible: Once a statically defined number of
detector simulations are packaged into a PBS job and this job is queued on
Titan, no further simulations can be added to that job. New simulations have
to be packaged into a new PBS job that needs to be submitted to Titan based 
upon backfill availability.

The support of  multiple generations of workload would enable a more efficient
use of the backfill availability of walltime. Currently, when a set of
simulations ends, the PBS job also ends, independent of whether more wall-time
would still be available. With a pilot, additional simulations could be
executed  to utilize all the available wall-time, while avoiding further job
packaging and submission overheads.

@@

\jhanote{not sure MPI script is optimal description or ambigious.} Multiple
generations would also relax two assumptions of the current execution model:
knowing the number of simulations before submitting the MPI script, and having
a fixed number of events per simulation (100 at the moment). Pilots would
enable the scheduling of simulations independently from whether they were
available at the moment of submitting the pilot. Further, simulations with a
varying number of events could be scheduled on a pilot, depending on the
amount of remaining walltime and the distribution of execution time per event,
as shown in \S\ref{ssec:panda_titan}, Figure~\ref{fig:100event- distrib}.
These capabilities would increase the efficiency of the PanDA Broker when
there is a large difference between the number of cores and walltime.

@@

% -----------------------------------------------------------------------------
\subsection{Implementation}
\label{sec:arch}
